What Can Stack Traces Tell us about Exceptions in Java?

### 2014-07-07 android-stacks.tex
changing title. testing commit wih a different user
changes on Introduction

\begin{document}
\title{What Can Stack Traces Tell us about the Use of Exceptions in Java?}

@@

Along the recent years we have witnessed a rapid increase in 
the number of open source software  available on the Web.
Since such projects make their control version and 
issue tracking systems publicly available, they represent a valuable 
source of information for the "state of practice" on software development
which had already started to be investigated [][][][][].

@@

Among these tools there is the Github issue tracking system, which makes
issues related to new features, improvements, bugs publicly available.

Bug issues have called the attention at have been the target of several 
researchs [][][]. A subtype of a bug issue are the ones related to system 
crashes [complete]...

>>>>

\begin{document}
\title{What Can Stack Traces Tell us about Exceptions in Java?}

@@

Along the recent years we have witnessed a rapid increase in 
the number of open source software  available on the Web.
Since such projects make their control version and 
issue tracking systems publicly available, they represent a valuable 
source of information for the "state of practice" on software development
which had already started to be investigated [][][][][][I still need to collect these references].

@@

Bug issues have called the attention of researhc community and  have been the target of several 
researches [][][]. A subtype of a bug issue are the ones related to system 
crashes, also called crash reports such reports can be automatically generated 
as the system crashes or can be manually reported by developers/users [complete]...
